Gravitational waves from colliding black holes

### 2017-05-01 Report/Draft/draft.tex
Draft latest

\begin{figure}[h]
	\includegraphics[scale=0.60]{fig1.jpg}
	\centering
	\caption{\cite{fig1}Plus and cross polarisations respectively of a gravitational wave propagating through the page, with scale greatly exagerrated.}
	\centering
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[scale=0.60]{fig2.jpg}
	\centering
	\caption{\cite{fig2}Impression of two inspiralling compact objects emitting gravitational waves}
	\centering
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[scale=0.60]{fig3.png}
	\centering
	\caption{Simulated waveform of a BBH merger of two 35 solar mass black holes.}
	\centering
\end{figure}

@@

The qualitative idea behind current methods of parameter estimation is that the GW signal is processed and extracted from the raw strain data, and then matched against an array of simulated waveforms to find which waveform most closely resembles the detected signal. The two technical challenges here are quantifying how well a template represents the observed signal, and how to efficiently sample the parameter space for new templates to test against the data. Within LIGO a standard method for quantifying the similarity between two signals $h_1(t)$ and $h_2(t)$ is given by the noise weighted inner product, also referred to as the 'match' between signals, and is defined as
\begin{equation}
\langle h_1(t) \vert h_2(t) \rangle=2\int_{0}^{\infty}\frac{\tilde{h_1^*}(f)\tilde{h_2}(f)+\tilde{h_1}(f)\tilde{h_2^*}(f)}{S_n(f)}df 
\end{equation}
where $\tilde{h}(f)$ is the Fourier transform of the signal $h(t)$, and $S_n(f)$ is the noise curve of the detector\cite{oldest_pe}. A variety of methods have been employed to sample the parameter space, including nested sampling\cite{pe2} and analysis using Gaussian wavelets\cite{props}, and in this work we use a framework of Bayesian inference and Markov-Chain Monte Carlo methods\cite{inj}\cite{pe}\cite{pe4}. This process results in a set of posterior distribution functions (PDFs) for each parameter. Using Bayes' Theorem, the posterior is given by
\begin{equation}
p(\vec{\theta})|d)=\frac{p(\vec{\theta})p(d|\vec{\theta})}{P(d)}
\end{equation}
where $\vec{\theta}$ is an $n$ dimensional vector in our parameter space of $n$ parameters\cite{pe2}. The first term in the numerator, $p(\vec{\theta})$ is known as the \textit{prior} distribution, and quantifies knowledge we already have about the system that should influence our estimation of its' parameters. In practice, in inference of BBHs, the priors are almost always uniform or isotropic distributions. The denominator, $P(d)$, is essentially a normalisation factor ensuring that the posterior distribution integrats to unity. The crucial term is the \textit{likelihood} for a given set of parameters given the data, which is determined by
\begin{equation}
p(d|\vec{\theta})\propto \exp\bigg(-\frac{1}{2}\sum_{k=1,2}\Big \langle h^M_k(\vec{\theta})-d_k \big\vert h^M_k(\vec{\theta})-d_k \Big \rangle\bigg)
\end{equation}
where the inner product is that defined in (13), $d_k$ is the observed strain in the detector, and $h_k^M(t;\vec{\theta})$ is the simulated detector response for a given set of parameters $\vec{\theta}$ given by (9).
Various methods of waveform generation (known as \textit{approximants}) have been attempted, with varying degrees of computational intensity. In general, Post-Newtonian expansions are used in the inspiral phase where the gravitational field is weak enough for approximations to be sufficient. During the merger and ringdown, full numerical relativity simulations are required as the curvature is sufficiently strong that Post-Newtonian approximations are no longer valid\cite{waveforms}\cite{imr}. These require significantly more computation time, and as such it is only in recent years that waveforms describing the full inspiral, merger and ringdown phases have become available.

@@

\subsection{Precession and its astrophysical importance}
Considerable research has been done on studying non-spinning binaries and on non-precessing binaries where the spins are aligned or anti-aligned with the orbital angular momentum $\vec{\hat{L}}$\cite{pe3}, but it is only recently that a more complete study of the parameter space has begun\cite{sloos}\cite{pe_latest}. This is partly down to computational resources, as ignoring spin effects leads to a reduced parameter space and less computationally intensive waveforms. There are a unique set of challenges when considering binaries where the spins of the component black holes are not aligned $\vec{L}$, as due to relativistic effects, these binaries precess around the axis of total angular momentum $\vec{\hat{J}}$, giving a time dependence to the orbital plane of the binary\cite{precess1}\cite{precess2}.
\begin{figure}[h]
	\includegraphics[scale=0.75]{fig6.jpg}
	\centering
	\caption{Illustration of a precessing binary system https://phys.org/news/2015-03-insights-black-hole-collisions.html}
	\centering
\end{figure}
This causes the signal in the detector to have an overall amplitude modulation as a function of time due to the change in orientation of the source, and therefore the change in direction of peak emission of GWs. This can be seen in Fig. 7, where we compare a very slightly precessing system with a maximally precessing one.
\begin{figure}[h]
	\includegraphics[scale=1]{fig7.png}
	\centering
	\caption{Waveforms for three BBH mergers with $m1=30$, $m2=10$ and with spins only in the $x$ direction on the heavier black hole. The inclination is such that the binary is viewed edge-on. LEGEND ON THIS FIGURE IS WRONG, FIX BEFORE SUBMIT}
	\centering
\end{figure}
Due to the computational intensity of dealing with both the generation of waveforms and inference process involving precessing systems, significant efforts have been made to reduce the size of the parameter space using the degenerecies between specific spin combinations to parametrise the spins of a binary. The most successful of these is the adoption of two spin parameters\cite{imr}\cite{chip} that describe the whole binary system, where we replace the six spin parameters with two:
\begin{equation}
\chi_{\text{eff}}=\bigg(\frac{\mathbf{S}_1}{m_1}+\frac{\mathbf{S}_2}{m_2}\bigg)\cdot\frac{\mathbf{\hat{L}}}{M}
\end{equation}
and
\begin{equation}
\chi_\text{p}=\frac{1}{B_1m^2_1}\text{max}(B_1S_{1\perp},B_2S_{2\perp})
\end{equation}
where $B1=2+3/(2q)$ and $B2=2+(3q)/2$. These parameters effectively quantify the amount of in-plane and out of plane spin of the total binary, removing large degenerate portions of the parameter space. As different spin configuations within these parameters are effectively degenerate, no loss of information occurs in this re-parametrisation. The recent adoption of this parametrisation in the generation of template waveform banks (the IMRPhenomPv2 waveforms which, we use in this work) has made exploring the precessing parameter space computationally viable, as it reduces the computation time by an order of magnitude. The results of these waveforms agree well when compared with waveforms generated using the full spin parameter space (known as the Spinning Effective One Body Numerical Relativity, or SEOBNR waveforms)\cite{spin}\cite{eob}, so the recent availability of a computationally efficient precessing waveform bank makes this an opportune time to conduct this research. Indeed the first full survey of an isotropic distribution of spins for a large number of simulations (200) has only very recently been published a matter of weeks ago\cite{pe_latest}.

@@

@@

\begin{figure}[h]
	\includegraphics[scale=0.58]{fig9.png}
	\centering
	\caption{Affect of phase on non-precessing and precessing waveforms. Precession adds an extra degree of freedom in that the morphology of precessing waveforms is different for different phases.}
	\centering
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[scale=0.55]{fig10.png}
	\centering
	\caption{Matches between precessing and non-precessing waveforms for a range of inclinations and mass ratios.(make this more compact before submit)}
	\centering
\end{figure}
\begin{figure}[h]
	\includegraphics[scale=0.55]{fig11.png}
	\centering
	\caption{Spin difference required for the match between precessing and non-precessing waveforms to drop below 0.95}
	\centering
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[scale=0.85]{fig12.png}
	\centering
	\caption{Match limit plots for a range of inclinations and phases for 4 polarisations.}
	\centering
\end{figure}

@@

A large number of software injections were going to be necessary to generate any interesting results due to the large size and complexity of the parameter space as revealed by the match results. So it was key that they could be performed efficiently and in an organised way. This required the construction of an inference pipeline which formed the bulk of the computational work of the project. This was ultimately one bash script that would create a new folder for each run, generate the injection file and run the inference MCMC.  It also saves the injected parameters as a python dictionary, plots all posteriors overlaid with injected parameters, plots the injected waveform, and the recovered (maximum posterior, or \textit{MAP} waveform) and injected waveforms overlaid on the whitened detector strain data, and return matches between the MAP and injected waveforms. This meant that all the relevant analysis and data processing needed for each inference run was fully automated. A flow chart of this process is shown in Fig. 12.

@@

\subsection{Inference runs}
In this section we present the results from a range of inference runs, attempt to assess the effectiveness of spin estimation and compare the inference results with the match results to evaluate how effective the match process is as a predictor of inference accuracy. For all injections we set $S_{1\perp}=0.9$ and $|\vec{S_2}|=0$ with $\chi_p=0.9$, and cover a uniform range of inclinations. We set the phase to be $\phi=0.$, and the polarisation angle $\psi=0.8$, so the signals are of mixed polarisation, but slightly cross dominated. The match results indicate that cross polarised signals generally have a higher spin resolution, but we want to avoid the signal drop at $\iota=\pi/2$, which is why a mixed but cross dominated polarisation angle was selected. The source location and coalesence time were also kept fixed for all injections. We also only examine high mass ratio binaries, as the match results indicate that precession is not significant in equal mass ratio binaries. Out of a total of ****** software injections that were performed, only **** instances where the injected $\chi_p$ value fell within the 90\% confidence interval. In Figs 14 and 15 we compare posteriors for two inferences, where $\chi_p$ was excluded and where it was recovered moderately well respectively. Even in the cases where the injected value was within the 90\% confidence intervals, it was always closer to the upper bound than to the mean, and a mean $\chi_p$ greater than 0.65 was never found.

@@

	\caption{Posteriors for an injection with $m1=50$, $m2=15$, $\iota=2.51$, $\phi=0$, $\psi=0.8$ at a distance of 200Mpc.}

@@

Neither sets of posteriors are consistently accurate, although overall the results in Fig. 14 are overall significantly more accurate than those in Fig. 15, with the exceptions of $\chi_p$ and $\iota$. The masses and source locations are recovered well, with the injected value lying within the 90\% confidence intervals. However the 'cost' of recovering $\chi_p$ seems to be having significant inaccuracies on a range of important parameters, with $\chi_{eff}$, $m2$, distance and chirp mass all being excluded. To examine the source of this inaccuracy, in Fig 16 we plot the whitened detector strain with the signal embedded into it, overlaid with the MAP waveform as recovered by the inference process, and the injected waveform. A match is also performed between the MAP and injected waveforms in each detector frame. This is a crucial part of the analysis, as it helps to distinguish between different sources of inaccuracy. If the inaccuracies are due to either detector noise or some error in the MCMC process, we should expect a low match between the MAP and injected waveform. However it is also possible that due to the large number of parameters, the MCMC algorithm has found certain combinations of different parameters that lead to an effectively degenerate waveform. In this case, we would expect a high match between the MAP waveform and injected waveform, despite the fact that they have vastly different parameters.
\subsection{Impact of Virgo}
A look at how Virgo will influence PE, especially chi p estimation.
\section{Conclusions and implications}
Summary of results on PE and estimation of chi p, and a prospect on Virgo's impact.
\section{Reflective Statement}
I now need a therapist

>>>>

\begin{figure}
	\includegraphics[scale=0.60]{fig1.jpg}
	\centering
	\caption{\cite{fig1}Plus and cross polarisations respectively of a gravitational wave propagating through the page, with scale greatly exagerrated.}
	\centering
\end{figure}

@@

\begin{figure}
	\includegraphics[scale=0.60]{fig2.jpg}
	\centering
	\caption{\cite{fig2}Impression of two inspiralling compact objects emitting gravitational waves}
	\centering
\end{figure}

@@

\begin{figure}
	\includegraphics[scale=0.60]{fig3.png}
	\centering
	\caption{Simulated waveform of a BBH merger of two 35 solar mass black holes.}
	\centering
\end{figure}

@@

The qualitative idea behind current methods of parameter estimation is that the GW signal is processed and extracted from the raw strain data, and then matched against an array of simulated waveforms to find which waveform most closely resembles the detected signal. The two technical challenges here are quantifying how well a template represents the observed signal, and how to efficiently sample the parameter space for new templates to test against the data. Within LIGO a standard method for quantifying the similarity between two signals $h_1(t)$ and $h_2(t)$ is given by the noise weighted inner product, also referred to as the 'match' between signals, and is defined as
\begin{equation}
\langle h_1(t) \vert h_2(t) \rangle=2\int_{0}^{\infty}\frac{\tilde{h_1^*}(f)\tilde{h_2}(f)+\tilde{h_1}(f)\tilde{h_2^*}(f)}{S_n(f)}df 
\end{equation}
where $\tilde{h}(f)$ is the Fourier transform of the signal $h(t)$, and $S_n(f)$ is the noise curve of the detector\cite{oldest_pe}. It is also convenient here to define the term \textit{mismatch}, which is simply $1-m$ where $m$ is the match. A variety of methods have been employed to sample the parameter space, including nested sampling\cite{pe2} and analysis using Gaussian wavelets\cite{props}, and in this work we use a framework of Bayesian inference and Markov-Chain Monte Carlo methods\cite{inj}\cite{pe}\cite{pe4}. This process results in a set of posterior distribution functions (PDFs) for each parameter. Using Bayes' Theorem, the posterior is given by
\begin{equation}
p(\vec{\theta})|d)=\frac{p(\vec{\theta})p(d|\vec{\theta})}{P(d)}
\end{equation}
where $\vec{\theta}$ is an $n$ dimensional vector in our parameter space of $n$ parameters\cite{pe2}. The first term in the numerator, $p(\vec{\theta})$ is known as the \textit{prior} distribution, and quantifies knowledge we already have about the system that should influence our estimation of its' parameters. In practice, in inference of BBHs, the priors are almost always uniform or isotropic distributions. The denominator, $P(d)$, is essentially a normalisation factor ensuring that the posterior distribution integrats to unity. The crucial term is the \textit{likelihood} for a given set of parameters given the data, which is determined by
\begin{equation}
p(d|\vec{\theta})\propto \exp\bigg(-\frac{1}{2}\sum_{k=1,2}\Big \langle h^M_k(\vec{\theta})-d_k \big\vert h^M_k(\vec{\theta})-d_k \Big \rangle\bigg)
\end{equation}
where the inner product is that defined in (13), $d_k$ is the observed strain in the detector, and $h_k^M(t;\vec{\theta})$ is the simulated detector response for a given set of parameters $\vec{\theta}$ given by (9).
Various methods of waveform generation (known as \textit{approximants}) have been attempted, with varying degrees of computational intensity. In general, Post-Newtonian expansions are used in the inspiral phase where the gravitational field is weak enough for approximations to be sufficient. During the merger and ringdown, full numerical relativity simulations are required as the curvature is sufficiently strong that Post-Newtonian approximations are no longer valid\cite{waveforms}\cite{imr}. These require significantly more computation time, and as such it is only in recent years that waveforms describing the full inspiral, merger and ringdown phases have become available.

@@

\subsection{Precession and its astrophysical importance}
Considerable research has been done on studying non-spinning binaries and on non-precessing binaries where the spins are aligned or anti-aligned with the orbital angular momentum $\vec{\hat{L}}$\cite{pe3}, but it is only recently that a more complete study of the parameter space has begun\cite{sloos}\cite{pe_latest}. This is partly down to computational resources, as ignoring spin effects leads to a reduced parameter space and less computationally intensive waveforms. There are a unique set of challenges when considering binaries where the spins of the component black holes are not aligned $\vec{L}$, as due to relativistic effects, these binaries precess around the axis of total angular momentum $\vec{\hat{J}}$, giving a time dependence to the orbital plane of the binary\cite{precess1}\cite{precess2}.
\begin{figure}
	\includegraphics[scale=0.75]{fig6.jpg}
	\centering
	\caption{Illustration of a precessing binary system https://phys.org/news/2015-03-insights-black-hole-collisions.html}
	\centering
\end{figure}
This causes the signal in the detector to have an overall amplitude modulation as a function of time due to the change in orientation of the source, and therefore the change in direction of peak emission of GWs. This can be seen in Fig. 7, where we compare a very slightly precessing system with a maximally precessing one.
\begin{figure}
	\includegraphics[scale=1]{fig7.png}
	\centering
	\caption{Waveforms for three BBH mergers with $m1=30$, $m2=10$ and with spins only in the $x$ direction on the heavier black hole. The inclination is such that the binary is viewed edge-on. LEGEND ON THIS FIGURE IS WRONG, FIX BEFORE SUBMIT}
	\centering
\end{figure}
Due to the computational intensity of dealing with both the generation of waveforms and inference process involving precessing systems, significant efforts have been made to reduce the size of the parameter space using the degenerecies between specific spin combinations to parametrise the spins of a binary. The most successful of these is the adoption of two spin parameters\cite{imr}\cite{chip} that describe the whole binary system, where we replace the six spin parameters with two:
\begin{equation}
\chi_{\text{eff}}=\bigg(\frac{\mathbf{S}_1}{m_1}+\frac{\mathbf{S}_2}{m_2}\bigg)\cdot\frac{\mathbf{\hat{L}}}{M}
\end{equation}
and
\begin{equation}
\chi_\text{p}=\frac{1}{B_1m^2_1}\text{max}(B_1S_{1\perp},B_2S_{2\perp})
\end{equation}
where $B1=2+3/(2q)$ and $B2=2+(3q)/2$. These parameters effectively quantify the amount of in-plane and out of plane spin of the total binary, removing large degenerate portions of the parameter space. As different spin configuations within these parameters are effectively degenerate, no loss of information occurs in this re-parametrisation. The recent adoption of this parametrisation in the generation of template waveform banks (the IMRPhenomPv2 waveforms which, we use in this work) has made exploring the precessing parameter space computationally viable, as it reduces the computation time by an order of magnitude. The results of these waveforms agree well when compared with waveforms generated using the full spin parameter space (known as the Spinning Effective One Body Numerical Relativity, or SEOBNR waveforms)\cite{spin}\cite{eob}, so the recent availability of a computationally efficient precessing waveform bank makes this an opportune time to conduct this research. Indeed the first full survey of an isotropic distribution of spins for a large number of simulations (200) has only very recently been published a matter of weeks ago\cite{pe_latest}.

@@

\begin{figure}

@@

\begin{figure}
	\includegraphics[scale=0.58]{fig9.png}
	\centering
	\caption{Affect of phase on non-precessing and precessing waveforms. Precession adds an extra degree of freedom in that the morphology of precessing waveforms is different for different phases.}
	\centering
\end{figure}

@@

\begin{figure}
	\includegraphics[scale=0.55]{fig10.png}
	\centering
	\caption{Matches between precessing and non-precessing waveforms for a range of inclinations and mass ratios.(make this more compact before submit)}
	\centering
\end{figure}
\begin{figure}
	\includegraphics[scale=0.55]{fig11.png}
	\centering
	\caption{Spin difference required for the match between precessing and non-precessing waveforms to drop below 0.95}
	\centering
\end{figure}

@@

\begin{figure}
	\includegraphics[scale=0.85]{fig12.png}
	\centering
	\caption{Match limit plots for a range of inclinations and phases for 4 polarisations.}
	\centering
\end{figure}

@@

A large number of software injections were going to be necessary to generate any interesting results due to the large size and complexity of the parameter space as revealed by the match results. So it was key that they could be performed efficiently and in an organised way. This required the construction of an inference pipeline which formed the bulk of the computational work of the project. This was ultimately one bash script that would create a new folder for each run, generate the injection file and run the inference MCMC.  It also saves the injected parameters as a python dictionary, plots all posteriors overlaid with injected parameters, plots the injected waveform, and the recovered (maximum posterior, or \textit{MAP} waveform) and injected waveforms overlaid on the whitened detector strain data, and return matches between the MAP and injected waveforms. This meant that all the relevant analysis and data processing needed for each inference run was fully automated. A flow chart of this process is shown in Fig. 12. For the MCMC parameters, in order to acheive a balance between computation time and result accuracy, 5,000 samplers were used and 12,000 iterations, and the burn-in process was skipped. These parameters were kept the same for all software injections.

@@

\subsection{Inference results}
In this section we present the results from a range of inference runs, attempt to assess the effectiveness of spin estimation and compare the inference results with the match results to evaluate how effective the match process is as a predictor of inference accuracy. For all injections we set $S_{1\perp}=0.9$ and $|\vec{S_2}|=0$ with $\chi_p=0.9$, and cover a uniform range of inclinations. We set the phase to be $\phi=0.$, and the polarisation angle $\psi=0.8$, so the signals are of mixed polarisation, but slightly cross dominated. The match results indicate that cross polarised signals generally have a higher spin resolution, but we want to avoid the signal drop at $\iota=\pi/2$, which is why a mixed but cross dominated polarisation angle was selected. The source location and coalesence time were also kept fixed for all injections. We also only examine high mass ratio binaries, as the match results indicate that precession is not significant in equal mass ratio binaries. Out of a total of ****** software injections that were performed, only **** instances where the injected $\chi_p$ value fell within the 90\% confidence interval. In Figs 14 and 15 we compare posteriors for two inferences, where $\chi_p$ was excluded and where it was recovered moderately well, and we refer to these as A and B respectively. Even in the cases where the injected value was within the 90\% confidence intervals, it was always closer to the upper bound than to the mean, and a mean $\chi_p$ greater than 0.65 was never found.
\begin{figure}

@@

	\caption{Posteriors for an injection with $m1=50$, $m2=15$, $\iota=2.51$, $\phi=0$, $\psi=0.8$ at a distance of 200Mpc. Prior distributions are included for the derived spin parameters $\chi_p$ and $\chi_{eff}$, which result from uniform spin magnitude and isotropic orientation distributions.}

@@

Neither sets of posteriors are consistently accurate, although overall the results of injection A are overall significantly more accurate than those for B, with the exceptions of $\chi_p$ and $\iota$. The masses and source locations are recovered well, with the injected value lying within the 90\% confidence intervals. However the 'cost' of recovering $\chi_p$ seems to be having significant inaccuracies on a range of important parameters, with $\chi_{eff}$, $m2$, distance and chirp mass all being excluded. To examine the source of this inaccuracy, in Fig 16 we plot the whitened detector strain with the signal embedded into it, overlaid with the MAP waveform as recovered by the inference process, and the injected waveform. A match is also performed between the MAP and injected waveforms in each detector frame. This is a crucial part of the analysis, as it helps to distinguish between different sources of inaccuracy. If the inaccuracies are due to either detector noise or some error in the MCMC process, we should expect a low match between the MAP and injected waveform. However it is also possible that due to the large number of parameters, the MCMC algorithm has found certain combinations of different parameters that lead to an effectively degenerate waveform. In this case, we would expect a high match between the MAP waveform and injected waveform, despite the fact that they have vastly different parameters.
	\includegraphics[scale=0.3]{fig16.png}
	\caption{Strain plots for both H1 and L1 detectors. The top two graphs show the strain data corresponding to the results in Fig. 14, the bottom two graphs correspond to Fig. 15. The green and red lines show the whitened strain data, the black line is the MAP waveform and the injected waveform is shown in blue.}

The results shown in Fig. 16 show a stronger match for A, where the majority of parameters were more accurately recovered. In particular, for B, L1 shows a low match of 0.93 between MAP and injected waveforms. This is likely due to the precessive effects which are most apparent around $~-0.4s$, where the injected signal is almost entirely flat, and later on during the inspiral around $~-0.2s$ where there is noteable disagreement between the signals. In this case, it is clear that the inference process has not found an optimal template waveform to replicate the injected signal. However in the case of A there is a strong match between waveforms, and it is clear from the strain plot that the MAP waveform matches the strain data extremely well. There is, however, a mild disagreement during the late merger and ringdown, which is the source of the mismatches of 0.01 and 0.02. Since the match is so strong, the waveforms themselves must be intrinsically degenerate up to deviation that occurs at the merger.

If two signals are degenerate for the majority of the inspiral and merger, and only during the end of the merger and ringdown do they differ, it will be extremely difficult for LIGO detectors to differentiate between them, as the very short time period where there is any mismatch will be swamped by noise. Returning to Fig. 14, we can see that even though the match is strong, there are significant inaccuracies on $\chi_p$ and $\iota$. So in results A and B we have examples of each inaccuracy as described earlier - one down to poor signal recovery and one down to an intrinsic degeneracy.
\subsection{Inclination and precession}
Next we examine the effect of inclination on $\chi_p$ recovery. Software injections were performed for a range of inclinations at two distances, 200Mpc and 800Mpc, which simulate a strong and weak signal respectively.
\subsection{Impact of Virgo}
A look at how Virgo will influence PE, especially chi p estimation.
\section{Conclusions}
Summary of results on PE and estimation of chi p, and a prospect on Virgo's impact.
\section{Reflective Statement}
I now need a therapist
